Generalized Plackett-Luce Likelihoods

### 2022-09-27 inst/jss_hyper3.Rnw
issue #162

<<label=converttosupp3, cache=TRUE>>=
javelin_vector <- attemptstable2supp3(javelin_table, decreasing=TRUE, give.supp=FALSE)
javelin_vector
@

@@

<<maxpconstructor2021, cache=TRUE>>=
const2020 <- ordertable2supp3(constructor_2020_table)
const2021 <- ordertable2supp3(constructor_2021_table)
maxp(const2020, n=1)
maxp(const2021, n=1)
@

@@

<<usesamep,cache=TRUE>>=
samep.test(H, c("Merc2020", "Merc2021"))
@

>>>>

<<label=converttosupp3, cache=TRUE>>=
javelin_vector <- attemptstable2supp3(javelin_table,
       decreasing=TRUE, give.supp=FALSE)
options(width=60)
javelin_vector
@

@@

<<maxpconstructor2021, cache=TRUE>>=
const2020 <- ordertable2supp3(constructor_2020_table)
const2021 <- ordertable2supp3(constructor_2021_table)
options(digits=4)
maxp(const2020, n=1)
maxp(const2021, n=1)
@

@@

<<usesamep,cache=TRUE>>=
options(digits=4)
samep.test(H, c("Merc2020", "Merc2021"))
@
